HBCC - ACC - STG - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-02 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix column header

## Download reprocessed counts (ACC and STG)
counts = 'syn21420322'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = counts
COUNT = downloadFile(counts) %>% data.frame()
COUNT$Chr <- NULL
COUNT$Start <- NULL
COUNT$End <- NULL
COUNT$Strand <- NULL

>>>>

## Download reprocessed counts (ACC and STG)
counts = 'syn21420322'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = counts
COUNT = downloadFile(counts) %>% data.frame()
COUNT$Chr <- NULL
COUNT$Start <- NULL
COUNT$End <- NULL
COUNT$Strand <- NULL
# Fix counts column header - remove "X" in sample name
new_names <- gsub("X6", "6", colnames(COUNT))
colnames(COUNT) <- new_names
